% !TeX root = ../../thesis.tex
\chapter{Abstract}                                 \label{ch:abstract}

This PhD thesis presents a comprehensive study of symmetry-protected topological (SPT) phases in quantum spin systems, focusing on their intriguing properties under various additional symmetries. The work is organized into two main papers, each contributing unique insights to the field of condensed matter physics.
\\\\
The thesis begins with a self-contained introduction into SPT order, which serves as a foundational understanding for subsequent discussions. Starting from finite-depth quantum circuits, the introduction provides essential background knowledge, laying the groundwork for exploring topological behaviors in quantum spin systems with symmetries.
\\\\
The first paper focuses on the classification of $G$-charge Thouless pumps within one-dimensional invertible states. These pumps describe loops of symmetry-protected topological (SPT) quantum states, characterized by continuous transformations of system parameters that bring the system back to its original state after completing a full loop. The paper systematically analyzes these loops for various symmetry groups, leading to a complete understanding of the classification of one-dimensional bosonic SPTs. Remarkably, this work generalizes the concept of Thouless pumps, encompassing cases where the symmetry group is $U(1)$ and classified by an integer representing the charge pumped per cycle.
\\\\
The second paper investigates two-dimensional quantum spin systems hosting SPT phases with on-site symmetry described by a finite group $G$. Through the imposition of translation invariance in different directions, the paper uncovers new topological invariants. Specifically, a new $H^2(G,\TT)$-valued index is discovered alongside the previously known $H^3(G,\TT)$-valued index. Additionally, when translation invariance is imposed in two directions, an extra $H^1(G,\TT)$-valued index emerges. The main contribution here is the mathematical rigor in the construction and the proof of stability of these indices.
\\\\
Both papers contribute significantly to the comprehension of topological behaviors in quantum spin systems with symmetries, showcasing the power of mathematical rigor in constructing and understanding topological invariants. The combination of rigorous analysis and accessible introductions ensures that the thesis is a valuable resource for researchers and students exploring the fascinating world of SPT phases in condensed matter physics.

%\ldots

%£\instructionsabstract


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Keep the following \cleardoublepage at the end of this file, 
% otherwise \includeonly includes empty pages.
\cleardoublepage

% vim: tw=70 nocindent expandtab foldmethod=marker foldmarker={{{}{,}{}}}
